---
title: "POTD 05 - Tibbles and Data Import"
author: "Simon Chen"
date: "11/23/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r task0}
# Import necessary libraries.
library(readr)
library(tidyverse)
# Import the data set.
aiw <- read_file(file = "https://www.gutenberg.org/files/11/11-0.txt")
```
## Task 1
Examine the first 3000 characters of aiw with str_sub().
```{r task1}
str_sub(aiw, 1, 3000)
```
## Task 2
Note that when imported, the text file brought along some formatting in the way of
"\n" and "\r" strings. Find and replace all such patterns with white space using str_replace_all().
```{r task2}
aiw <- str_replace_all(aiw, "\n", " ")
aiw <- str_replace_all(aiw, "\r", " ")
str_sub(aiw, 1, 3000)
```

## Task 3
Project Gutenberg has added some text at the beginning and appended some legal
boilerplate text to the end. Find the true beginning and ending of the text and save only the
book text (i.e., drop off the boilerplate). Save this as aiw2.
```{r task3a}
# Drop the boilerpate
str_locate_all(pattern = "Alice’s Adventures in Wonderland", aiw)
```
```{r task3b}
# Find the end
str_locate_all(pattern = "THE END", aiw)
```
```{r task3c}
aiw2 <- str_sub(aiw, 900, 148854)
str_sub(aiw2, 1, 3000)
```
```{r task3d}
str_sub(aiw2, 147800, str_length(aiw2))
```


## Task 4
Note that aiw2 is a single long character string. We would like to separate the words
so that each is it’s own element of a character vector. So, once Task 2 is accomplished, use
str_split() to do that and rename the result to aiw3. This will produce output in a list,
but we want a vector, so use unlist() on aiw3 to turn it into a long character vector; again,
save the output as aiw3 here.
```{r task4}
aiw3 <- unlist(str_split(aiw, boundary("word")))
aiw3[1:20]
```
## Task 5
What proportion of words in the book contain at least one uppercase letter?
```{r task5}
mean(str_detect(aiw3, "[A-Z]+"))
```

## Task 6
What proportion of words in the book use some form of punctuation?
```{r task 6}
mean(str_detect(aiw3, "[[:punct:]]+"))
```
## Task 7

Alice in Wonderland is one of the most influential books for children written over the
past 200 years. As an example, ever wonder why Nintendo’s Super Mario grows when he eats
a mushroom? Although Shigeru Miyamoto (Mario’s creator) has more recently denied a direct
influence, he has spoken in the past about how he was thinking about Alice in Wonderland
while creating the video game. How many times does the word "mushroom" occur in the
text, regardless of letter case? Locate each instance of the word and print out enough of the
surrounding text to display the context for each instance.

```{r task 7a}
sum(str_detect(aiw3, "(?i)mushroom"))
```
```{r task 7b}
# Locate
loc <- which(str_detect(aiw3, "(?i)mushroom") == TRUE)
loc
```
```{r task 7c}
aiw3[8803:8850]
```
```{r task 7d}
aiw3[8852:8900]
```

```{r task 7e}
aiw3[9912:9950]
```
```{r task 7f}
aiw3[9960:9980]
```
```{r task 7g}
aiw3[10870:10900]
```
```{r task 7h}
aiw3[13633:13700]
```
```{r task 7i}
aiw3[15961:16000]
```