---
title: "Wrangle the data"
author: "Simon Chen"
date: "11/23/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Wrangle the data
Upload code for importing and cleaning your 
data along with any necessary data transformation, recoding, handling of 
missingness, factors and dates, or other wrangling issues. 

```{r task0}
# import certain library
library(tidyverse)
library(ggplot2)
```
```{r task1}
# Read data and import it as tibble.
dat <- read_csv("PTSD_Outcomes_Within_Each_Treatment_Arm.csv")
dat <- tibble(dat)
dat
```
## Dealing with missing data.
Since there are too many missing data and they are irrelevant to the anlysis.
So we can just drop the missing cases.
```{r task2}
drop_na(dat)
dat
```
## Selcet columns
```{r task3}
# Since the we need to make our analysis more convincible, we need to use total N randomized more than 100.
names(dat)[names(dat) == 'Treatment Focus (Arm level)'] <- 'Treatment'
names(dat)[names(dat) == 'Total N Randomized'] <- 'Total'
dat2 <- select(dat, study_id, Treatment, Total, "N Completed Outcome Measurement", "Measure Score Mean", "Year Added to PTSD-Repository")
dat2 <- filter(dat2, Total >= 100)
dat2
```
Then the data should be ready to analyze.