---
title: "POTD 02 - Data Visualization"
author: "Simon Chen"
date: "10/4/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Task 1

Access the help on the data set `state.x77` and briefly describe the data. Convert it to a data frame (tibble) with `as_tibble()`. For example, `dat <- as_tibble(state.x77)`. Now work with the data called dat.

```{r task1}
library(tidyverse)
# Check the state.x77 data set.
?state.x77
#state.x77: matrix with 50 rows and 8 columns giving the following statistics in the respective columns. Population: population estimate as of July 1, 1975. Income: per capita income (1974). Illiteracy: illiteracy (1970, percent of population). Life Exp: life expectancy in years (1969–71). Murder: murder and non-negligent manslaughter rate per 100,000 population (1976). HS Grad: percent high-school graduates (1970). Frost: mean number of days with minimum temperature below freezing (1931–1960) in capital or large city. Area:land area in square miles. 

# Convert it to a data frame (tibble) with as_tibble().
dat <- as_tibble(state.x77)
dat
```

## Task 2

Make a scatterplot of murder rate (on x-axis) and life expectancy (on y-axis).

```{r task 2}
# Show the variables name to check potential space error.
names(dat)
# To rename variables for indexing
names(dat)[4] <- 'Life_exp'
# To plot with murder and life exp.
ggplot(data = dat) + 
  geom_point(mapping = aes(x = Murder, y = Life_exp))
```

## Task 3

Access the help on `state.region` and `state.division` and `state.abb`. Briefly
describe them each.

```{r task 3}
?state
```
state.region: factor giving the region (Northeast, South, North Central, West) that each state belongs to.</br>
state.division: factor giving state divisions (New England, Middle Atlantic, South Atlantic, East South Central, West South Central, East North Central, West North Central, Mountain, and Pacific).</br>
state.abb: character vector of 2-letter abbreviations for the state names.</br>

## Task 4

Building on the scatterplot you made above in (2), color the points by state region.
```{r task 4}
ggplot(data = dat) +
  geom_point(mapping = aes(x = Murder, y = Life_exp, color = state.region))
```

## Task 5

Building on the scatterplot you made above in (2), create a faceted plot by state division.

```{r task 5}
ggplot(data = dat) +
  geom_point(mapping = aes(x = Murder, y = Life_exp)) +
               facet_wrap(state.division)
```

## Task 6

Building on the scatterplot you made above in (2), add a nonparametric regression (loess) curve with standard error bars.

```{r task 6}
ggplot(data = dat, mapping = aes(x = Murder, y = Life_exp)) +
  geom_point() + 
  geom_smooth()
```

## Task 7

Building on the scatterplot you made above in (2), add a nonparametric regression (loess) curves by state region and also color the curves but not the points by state region.

```{r task 7}
ggplot(data = dat, mapping = aes(x = Murder, y = Life_exp)) +
  geom_point() + 
  geom_smooth(mapping = aes(color = state.region))
```

## Task 8

Task 8 Flex your muscles :) In other words, do something creative with the `state.x77` data (and possibly also the other variables like region, etc.) that demonstrates your new expertise in plotting with `ggplot2`.

```{r task 8}
# To find relations between life_exp and income using box plot.
ggplot(data = dat, mapping = aes(x = state.region, y = Income)) +
         geom_boxplot()
# We can tell that boxplot for the region and income is not obvious, so we have to choose the correct tool to do analysis.
```
