---
title: "POTD 04"
author: "Simon Chen"
date: "10/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Run the following code to create a tibble using the `state.x77` data. <br>

```{r task0}
# Import libraries.
library(tidyverse)
library(ggplot2)
library(magrittr)

# Load the dataset and create a tibble.
dat <- data.frame(state.x77)
dat <- tibble(dat)

# Add the region and division and abbreviation information
dat$Region <- state.region
dat$Division <- state.division
dat$abbrev <- state.abb
print(dat, n = 50, width = 100)
```

## Task 1

Create a histogram of life expectancy (i.e., including data from all 50 states).<br> Did
you use binwidth = or bins = and how did you decide on the value?


```{r task 1}
ggplot(data = dat, mapping = aes(x=Life.Exp)) +
  geom_histogram(binwidth = 0.5) +
  xlab('Life Expectancy') +
  ylab('counts')
```

## Task 2

Use group_by() and summary() to determine mean life expectancies and HS grad-
uation rates for each region.

```{r task 2}
group_by(dat, Region) %>%
  summarise(avg_LE = mean(Life.Exp, na.rm = TRUE), 
            avg_HS_rate = mean(HS.Grad, na.rm = TRUE))
```

## Task 3

Use frequency polygons to create histograms of life expectancy by color based on state
region, both by count and using density. <br>Which do you prefer for these data and why?

I still preferred the counts one, because it's obviously clear to show the difference.
```{r task 3}
#by counts
ggplot(data = dat, mapping = aes(Life.Exp, color = Region)) +
  geom_freqpoly(binwidth= 0.5) + 
  xlab("Life Expectancy") + 
  ylab("counts")

#by density
ggplot(data = dat, mapping = aes(Life.Exp, after_stat(density), color = Region)) +
  geom_freqpoly(binwidth= 0.5) + 
  xlab("Life Expectancy") + 
  ylab("density")
```

## Task 4

Create conditional box plots of life expectancy by state region (i.e., using the same
information as in the previous task). <br> What are the pros/cons to using boxplots vs frequency
polygons here and in general?

Pros: it can clearly show the range of the data, and mean.
cons: But the comparison between then is not clear.
```{r task 4}
ggplot(data = dat, mapping = aes(Region, Life.Exp)) +
  geom_boxplot() + 
  ylab("Life Expectancy") + 
  xlab("Region")
```
## Task 5
Replicate the last plot but also order the boxplots by their medians.

```{r task 5}
ggplot(data = dat, mapping = aes(x=reorder(Region, Life.Exp, FUN = median), y=Life.Exp)) +
  geom_boxplot() + 
  ylab("Life Expectancy") + 
  xlab("Region")
```

## Task 6
Create a scatterplot of HS graduation rate on the horizontal axis and life expectancy
on the vertical axis.

```{r Task 6}
ggplot(data = dat, mapping = aes(x = HS.Grad, y = Life.Exp)) +
  geom_point() + 
  ylab("Life Expectancy") + 
  xlab("High School Graduation Rate")
```

## Task 7
Replicate the scatterplot directly above using two-letter state abbreviations instead of
points for plotting.
```{r Task 7}
ggplot(data = dat, mapping = aes(x = HS.Grad, y = Life.Exp)) +
  geom_text(aes(label = abbrev)) + 
  ylab("Life Expectancy") + 
  xlab("High School Graduation Rate")
```

## Task 8

Note that AK and NV are outlying. Use filter(), as in lines 163–169 of ’04_Code.R’,
to color those two points blue.
```{r Task 8}
temp <- dat%>% 
  filter(abbrev %in% c("AK", "NV"))

ggplot(data = dat, mapping = aes(x = HS.Grad, y = Life.Exp)) +
  geom_text(aes(label = abbrev)) + 
  geom_text(data = temp, mapping = aes(x=HS.Grad, y = Life.Exp, label = abbrev), color = "blue") +
  ylab("Life Expectancy") + 
  xlab("High School Graduation Rate")
```

## Task 9

Import your project data into R and make a plot of some kind.

Reading data is fine but I need to sort the data then plot them...
```{r Task 9}
# Reading csv data
dat <- read_csv("PTSD_Outcomes_Within_Each_Treatment_Arm.csv")
dat <- tibble(dat)

ggplot(data = dat, mapping = aes(x = study_id, y = "Total N Randomized")) +
  geom_point() + 
  ylab("Total N Randomized") + 
  xlab("Study ID")
```
