---
title: "Describe variables"
author: "Simon Chen"
date: "10/26/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Describe the variables you are interested in 
working with – there should be around 5, at least one numeric and at least one 
factor, but a few more is fine. The descriptions should include information on the 
data type for each variable (numeric or factor), the range of values, and some type 
of tabular or graphical summary (crosstabs, histogram, boxplot, scatterplot, etc.). 

## Variables

1. Study Class <Text>:<br>
Describes top-level classification of the study as: Psychotherapy, Pharmacotherapy, CIH, Nonpharm biologic, Nonpharm cognitive, Collaborative Care, Psychotherapy & Pharmacotherapy, Psychotherapy & CIH, Other Mixed.<br>
I will try to measure the effectiveness of each treatment method

2. Total N Randomized <Number>:<br>
Total participants randomized in the study (total of all arms).
The range is [8, 943], we can see the distribution in different study class.

```{r task 1}
library(tidyverse)
# Import the data
dat <- read.csv('PTSD_Outcomes_Within_Each_Treatment_Arm.csv')
dat <- tibble(dat)
# Rename some columns
dat

ggplot(data = dat, aes(x = Study.Class, y = Total.N.Randomized)) + 
  geom_point()
```