---
title: "POTD 03 - Markdown"
author: "Simon Chen"
date: "10/12/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


Run the following code to create a tibble using the `state.x77` data. <br>

```{r task0}
# Import libraries.
library(tidyverse)
library(ggplot2)
library(magrittr)

# Load the dataset and create a tibble.
dat <- data.frame(state.x77)
dat <- tibble(dat)

# Add the region and division and abbreviation information
dat$Region <- state.region
dat$Division <- state.division
dat$abbrev <- state.abb
print(dat, n = 50, width = 100)
```

## Task 1

Create a scatterplot of life expectancy on the horizontal and illiteracy rate on the vertical and color the point by state region.


```{r task 1}
ggplot(data = dat, mapping = aes(x=Life.Exp, y=Illiteracy, color=state.region)) +
  geom_point() +
  xlab('Life Expectancy') +
  ylab('Illiteracy Rate')
```

## Task 2

Now, instead of using **geom_point()**, use **geom_text** to create the same plot as above but with the state abbreviations plotted for each point instead of circles. It should look like this:

```{r task 2}
ggplot(data = dat, mapping = aes(x=Life.Exp, y=Illiteracy, color=state.region)) +
  geom_text(aes(label=abbrev)) +
  xlab('Life Expectancy') +
  ylab('Illiteracy Rate')
```

## Task 3

Filter the data set to include only states that have illteracy rates higher than 1.6 and life expectancies lower than 75. Verify visually that your results agree with your plot.

```{r task 3}
# Filter the data
f_dat <-filter(dat, Illiteracy > 1.6, Life.Exp < 75)
# Verify
ggplot(data = f_dat, aes(x=Life.Exp, y=Illiteracy)) +
  geom_text(aes(label=abbrev)) +
  xlab('Life Expectancy') +
  ylab('Illiteracy Rate')
```

## Task 4

Create a data set that only contains Hawaii by filtering on region and life expectancy.

```{r task 4}
hawaii_dat <- filter(dat, Region == 'West', Life.Exp == 73.6)
hawaii_dat
```
## Task 5

Arrange the data, first in ascending then in descending order, based on state area. <br>
Which are the three states with most area? Which are the three states with least area?

```{r task 5}
# Ascending order.
asc_dat <- arrange(dat, Area)
print(head(asc_dat, 3))
print(head(asc_dat, 3)$abbrev)

# Descending order.
des_dat <- arrange(dat, desc(Area))
head(des_dat, 3)
```

## Task 6
Use mutate() to add a variable to the data frame that gives state area in square kilometers (instead of square miles).

```{r Task 6}
dat <- mutate(dat, Area_in_square_km = Area * 2.59)
```

## Task 7
Create a data frame with four variables: state population, state area, the number of people per square mile and the number of people per square kilometer.
```{r Task 7}
four_dat <- mutate(dat, pop_per_square_mile = Population / Area,
         pop_per_square_km = Population / Area_in_square_km) %>%
  select(Population, Area, pop_per_square_mile, pop_per_square_km)
head(four_dat)
```

## Task 8
I want to use count function to get a gist of this data.
```{r Task 8}
count(population)
```
