---
title: "POTD 01 - Markdown"
author: "Simon Chen"
date: "9/21/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Task 1

Demonstrate some arithmetic in R using `+,-,*,/,(), and ^`.


```{r task1}
# Demonstrate +
1 + 2
# Demonstrate -
1 - 2
# Demonstrate *
1 * 2
# Demonstrate /
1 / 2
# Demonstrate ()
(1+2) * 3
# Demonstrate ^
2 ^ 3
```

## Task 2

Going beyond the **division operator**.

a) What does the **%%** operator do? See if you can figure it out via trial and error by running it with a bunch of numbers. 
For example,`5 %% 2`. Then confirm your guess by looking it up online and/or with help, as in help(**’%%’**).

* I assume that %% returns the reminder, the mod operations.
```{r task 2a}
# Mod operator
x <- 1
x == 5 %% 2
```

b) What does the **%/%** operator do?

* %/% indicates integer division.
```{r task 2b}
# Integer division.
x <- 2
x == 5 %/% 2
```

## Task 3

Write some comments in R using #'s

*I had comments for each code chunk.*

## Task 4

Use the **c()** function to create the following:

a) A numeric vector of length 5.

```{r task 3a}
x <- c(1:5)
x
```

b) A logical vector of length 3.

```{r task 3b}
x <- c(TRUE, FALSE, TRUE)
x
```

c) A character vector of length 4.
```{r task 3c}
x <- c('Hello', 'World', '!', 'Simon')
x
```

## Task 5 

Create vector sequences using **seq()** and **rep()** and demonstrate how the
functions work and explain their arguments.

```{r task 5a}
x <- seq(from = 1, to = 10, by = 1)
x
```
seq() generates regular sequences, **'seq'** is a standard generic with a default method. 

from, to arguments are the start and end of the sequence, and by is the increments/decrements.

```{r task 5b}
x <- rep(c(1,2,3), times = 3, each = 2)
x
```
rep() generates repeating objects.
The first parameter is the variable, times is how many times you want to repeat,
each is in each time, how many elements you want to have.

## Task 6 

Use **rep()** to generate the following vectors:

a) 15 15 10 10 25 25 15 15 15 15 10 10 25 25 15 15 15 15 10 10 25 25 15 15

```{r task 6a}
x <- rep(c(15, 10, 25, 15), times = 3, each = 2)
y = c(15, 15, 10, 10, 25, 25, 15, 15, 15, 15, 10, 10, 25, 25, 15, 15, 15, 15,
      10, 10, 25, 25, 15, 15)
x
setequal(x,y)
```

b) 15 15 15 10 10 10 25 25 25 15 15 15 15 15 15 10 10 10 25 25 25 15 15 15
```{r task 6b}
x <- rep(c(15, 10, 25, 15), times = 2, each = 3)
y <- c(15, 15, 15, 10, 10, 10, 25, 25, 25, 15, 15, 15, 15, 15, 15, 10, 10, 10,
       25, 25, 25, 15, 15, 15)
x
setequal(x,y)
```

## Task 7

Create some variable names using assignment arrows, **<-** , use them in arithmetic,
and print the results. As an example

x <- 15

y <- x + 12

z <- x*y

x

y

z

x + y + z

```{r task 7}
# Create a task6 and task7 vectors.
task6 <- 6
task7 <- 7
# Arithmetic operations
task1 <- task6 + task7
task2 <- task6 * task7
task3 <- task6 - task7
task4 <- task6 / task7
task5 <- task6 %% task7

# print out the results.
task1
task2
task3
task4
task5
task6
task7
```
